dispRity ecology demo

### 2017-12-20 inst/gitbook/07_ecology-demo.Rmd
v0.5 gitbook

---
title: "dispRity ecology demo"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: References.bib
bst: sysbio.bst
vignette: >
  %\VignetteIndexEntry{dispRity ecology demo}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

@@

```{r}
## Fitting a linear model to our data
disparity_lm <- test.dispRity(petal_disparity, test = lm, comparisons = "all")

## Testing whether there is a difference in disparity between the different species
summary(aov(disparity_lm))

>>>>

---
title: "dispRity ecology demo"
author: "Thomas Guillerme"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: [References.bib, packages.bib]
bst: sysbio.bst
vignette: >
  %\VignetteIndexEntry{dispRity ecology demo}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

@@

```{r}
## Running a PERMANOVA
test.dispRity(petal_disparity, test = adonis.dispRity)
